---
title: "Edinburgh Inside Airbnb"
date: "9/18/2019"
output: github_document
---

Recent development in Edinburgh regarding the growth of Airbnb and its impact on the housing market means a better understanding of the Airbnb listings is needed. Using data provided by Airbnb, we can explore how Airbnb availability and prices vary by neighborhood.

The data come from the [Kaggle database](https://www.kaggle.com/thoroc/edinburgh-inside-airbnb/version/2).

We'll use the **tidyverse** and the **ggridges** packages for this analysis.

```{r load-packages, message=FALSE}
library(tidyverse)
library(ggridges)
```

The dataset we'll be working with is called `listings.csv`.

```{r load-data, message=FALSE}
listings <- read_csv("data/listings.csv")
```

## Airbnb listing prices

There are `r nrow(listings)` observations in this dataset. We'll start by visualizing the price data.

```{r overall-hist, fig.height=3}
ggplot(data = listings, mapping = aes(x = price)) +
  geom_histogram(binwidth = 50) +
  labs(
    title = "Daily prices of Airbnb listings in Edinbugh",
    x = "Price, in $"
    )
```

There appears to be some really expensive listings! What are they?

```{r view-expensive}
listings %>%
  arrange(desc(price)) %>%
  select(price, neighbourhood, accommodates, listing_url)
```

## Prices by neighborhood

Next we plot the price distributions by neighborhood. The following shows 
density plots for each neighbourhood. This representation is also called 
a ridge plot.

```{r neighbourhood-ridge, fig.height=5, message=FALSE}
ggplot(data = listings, 
       mapping = aes(x = price, y = neighbourhood, fill = neighbourhood)) +
  geom_density_ridges(alpha = 0.7, scale = 4) +
  guides(fill = "none") +
  labs(
    title = "Daily prices of Airbnb listings in Edinbugh, by neighbourhood",
    x = "Price, in $"
    )
```

We can also take a look at box plots.

```{r neighbourhood-box}

```

And calculate summary statistics like number of listings, and mean and 
median prices by neighborhood.

```{r neighbourhood-median}

```


